\documentclass[conf,hidelinks]{new-aiaa} % insert '[draft]' option to show overfull boxes
%---------- USER-ADDED PACKAGES
\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage{booktabs} 	% For tables
\usepackage{breqn}
\usepackage{caption} 	% For subfigures
\usepackage[capitalise]{cleveref}
\usepackage{color,soul} % For coloring text
\usepackage{subfigure}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{import}		% Package for breaking down lengthy documents into submodules
\usepackage{pdfpages} 	% To include PDF pages in appendix
\usepackage{placeins}	% Floatbarrier
\usepackage{siunitx} 	% For the degree symbol "\ang{}"
\usepackage{titlesec}
\usepackage{todonotes}
\usepackage{type1cm}
\usepackage{wasysym}
\usepackage{wrapfig}	% For inline figures
\makeatletter
\makeatother
% ---------------------------------
% Variables
\newcommand{\figwidth}{3.4in}				% Width of single figure
\newcommand{\figheight}{2.43in}				% Height of single figure
\newcommand{\figwidthlegend}{4.0in}			% Width of single figure with outer legend
\newcommand{\doubfigf}{.475}				% Text width factor in double figure
\AtBeginDocument{\renewcommand{\abstractname}{}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COVER PAGE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Method Comparisons for Wake Model and Optimization Algorithm Selection in Wind Farm Layout Optimization}

\author{Nicholas F. Baker\footnote{Masters Student, Department of Mechanical Engineering, 360 EB, Provo, UT 84602, AIAA Student Member},
		 Andrew P. J. Stanley\footnote{Ph.D. Candidate, Department of Mechanical Engineering, 360 EB, Provo, UT 84602, AIAA Student Member},
		 and Andrew Ning\footnote{Assistant Professor, Department of Mechanical Engineering, 360 EB, Provo, UT 84602, AIAA Senior Member}}
	\affil{Brigham Young University, Provo, Utah 84602.}
\author{Katherine Dykes\footnote{DTU}}
	\affil{Danmarks Tekniske Universitet, 2800 Kgs. Lyngby, Denmark.}

\begin{document}
\maketitle{}

\import{./sections/}{iea37-cs34-abst.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

	\import{./sections/}{iea37-cs34-intro.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% METHODOLOGY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology} \label{sec:meth}

	\import{./sections/}{iea37-cs34-mthd.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% RESULTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results} \label{sec:res}

	\import{./sections/}{iea37-cs34-rslts.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Conclusion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion} \label{sec:conc}

	\import{./sections/}{iea37-cs34-conc.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%							APPENDIX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
\appendix

\section*{Acknowledgments}
This work was authored [in part] by the National Renewable Energy Laboratory, operated by Alliance for Sustainable Energy, LLC, for the U.S. Department of Energy (DOE) under Contract No. DE-AC36-08GO28308.
Funding provided by the U.S. Department of Energy Office of Energy Efficiency and Renewable Energy Wind Energy Technologies Office.
The views expressed in the article do not necessarily represent the views of the DOE or the U.S. Government.
The U.S. Government retains and the publisher, by accepting the article for publication, acknowledges that the U.S. Government retains a nonexclusive, paid-up, irrevocable, worldwide license to publish or reproduce the published form of this work, or allow others to do so, for U.S. Government purposes.

The authors gratefully acknowledge the following individuals, in alphabetical order, as submitting participants in the case study:
\begin{itemize}
	%\item name (organization), etc
	\item Tim Camp, Director, Turbine Engineering
	\item Abhinav Prakash, Ph.D. Student, Texas A\&M University
	\item Erik Quaeghebeur, Dr.ir, Delft University of Technology
	\item Sebastian, Sanchez Perez Moreno, Ph.D. Student, Delft University of Technology
	\item Landon Wiley, M.Sc Student, Brigham Young University
\end{itemize}

\newpage
\section*{Appendix}

%\section{Python Code}
%\label{app:aepcalc}
%\lstinputlisting[language=python]{iea37-aepcalc.py}

\FloatBarrier

\pagebreak
%\bibliographystyle{new-aiaa}
\bibliography{aiaa-jrnl}
\end{document}