			
	% This is how we did it
To enable production of useful data, our case studies would require a model wind farm with characteristics that are simultaneously restrictive enough to maintain simplicity, yet general enough to maintain relevance to more complex and realistic problems.
The wind farm scenarios we selected to meet this criteria, and other details relevant to this project as a whole, are described below in \cref{sec:windfarm}.

Many factors affect reccomendations for superior turbine placement of a proposed wind farm.
Two of the major factors which we chose to study are
1) EWM characteristics and 2) optimization algorithm.\cite{HerbertAcero2014}
We therefore designed two case studies in an attempt to quantify the effects of alterations in each of these variables.

For the first case study, in which the goal was to isolate variability in the optimization method, we pre-coded a representative wake model as a control variable,
and permit participants to use any optimization strategy they think will discover turbine locations which deliver the best Annual Energy Production (AEP) for the farm.
This is called the Optimization Only Case Study, and is described below in \cref{sec:optonly}.

Isolating EWM variability proves more complicated.
An EWM's compatibility with gradient-based or gradient-free optimization methods dictate which algorithms can be applied.
As such, designing a case study that restricts participants to a single optimization algorithm would unnecessarily limit the scope of EWMs studied.
For this reason, our second case study permits not only participant selection of EWM, but also implemented optimization algorithm.
It is called the Combined Physics Model/Optimization Algorithm Case Study, and is described below in \cref{sec:cmbnd}.

\bigskip
\subsection{Common to Both Case Studies} \label{sec:windfarm}

	\import{./sections/}{iea37-wflocs-mthd-bothcs.tex}
	
\subsection{Optimization Only Case Study} \label{sec:optonly}

	\import{./sections/}{iea37-wflocs-mthd-optonly.tex}

\subsection{Combined Physics Model/Optimization Algorithm Case Study} \label{sec:cmbnd}

	\import{./sections/}{iea37-wflocs-mthd-cmbnd.tex}