%-- This is so far unaltered from the extended abstract you submitted --%
\begin{abstract}
	\textbf{This paper presents the results of two case studies regarding the Wind Farm Layout Optimization (WFLO) problem.
		Case study (1) considers variations in optimization strategies for a given simplified Bastankhah Gaussian wake model, while case study (2) studies trade offs in performance with variation in both physics model and optimization strategy selection.
		For (1), a supplied wake model outputs Annual Energy Production (AEP) given participant input turbine locations.
		For (2), participants calculate AEP using a wake model of their choice, while also implementing their preferred optimization method.
		%Participant submissions for optimized turbine locations were then compared to Large Eddy Simulator (LES) calculations for AEP, and results were measured for both quality and accuracy.
		Participant submissions for optimized turbine locations were then cross-compared through one another's wake models.
		Results for (1) show that the best optimal wind farm layouts in this study were achieved by participants that used gradient-based optimization methods.
		A clear front-runner emerged with the SNOPT \texttt{+} WEC optimization method, which consistently discovered a comparative optimal AEP for each scenario.
		Results for (2) show that for small windfarms with few turbines, turbine placement on the wind farm boundary is superior.
		Conclusions for (2) were drawn from participant cross-comparison of results.%, but further study must be done using an LES analysis of participant turbine layouts.
		}
\end{abstract}